---
title: "Ruble package vignette"
author: "Alexey Antonitsin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## stock_pick

This function will take a sample (stocks_lim) of tickers and pull their returns data. Then it will
run the optimal allocation portofolio to allocate the budget between this stocks most efficiently.

The function also chekcs if the ticker is still available on Yahoo Finance and if the ticker existed on a 
given date.
```{r, echo=FALSE, results='asis'}
Ruble::stock_pick()
```

Alternatively, if stock tickers are supplied, the function will try to allocate budget between funds.
```{r, echo=FALSE, results='asis'}
Ruble::stock_pick(c("EBAY", "AMZN"))
```


## rent_or_buy
This function goal is to help make a decision to buy or to rent a house. Function has a lot of arguments with default values.
Also Shiny dashboard is available for visualization the results.

Output is a chart that demonstrates 2 curves: one for renting and another for buying.
```{r}
Ruble::rent_or_buy()
```
